---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
install.packages("corrplot")
library(tidyverse)
library(corrplot)

```


## Topic 1

### Exercise 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:


```{r}

mydata <- read.csv("MET Office Weather Data.csv")
mydata
```

```{r}
mydata_cor <- select(mydata, rain, tmax,
                             tmin, af)
M <- cor(mydata_cor, use="pairwise.complete.obs")
corrplot(M, method = "shade")


```

```{r}
set.seed(1)
training_set <- sample(seq_len(nrow(mydata)), size = floor(0.75 * nrow(mydata)))
train <- mydata[training_set, ]
test <- mydata[-training_set, ]
```


## Model 1

dependent: rain
Indepenent: Max Temperature

question dose on the max temperature have any effect on the amount of rain fall 

```{r}
model1 <- lm(tmax ~ rain,mydata)
test1 <- data.frame(rain = c(6))
predictMaxTemp <- predict(model1, test1)
cat("The Max Temp (c) in UK will be: ", predictMaxTemp , "(c).")

```
```{r}
ggplot(mydata, aes(x= rain, y= tmax))+
  geom_point(aes(color = tmax ))+
  theme(legend.position = "none")+
  labs(title = "Rain vs Max Temperature", subtitle = "UK 1853 - 2020",
       x = "Rain Fall C°", y = "Max Temperature C°")
```
seems like rain fall is slowly going down in the uk



##Model 2

dependent: rain
Indepenent: Min Temperature

```{r}
model2 <- lm(tmin ~ rain,mydata)
test2 <- data.frame(rain = c(6))
predictMinTemp <- predict(model2, test2)
cat("The Min Temp (c) in UK  will be:", 
    predictMinTemp , "(c).")
```




```{r}
ggplot(mydata, aes(x= rain, y= tmin))+
  geom_point(aes(color = tmin))+
  theme(legend.position = "none")+
  labs(title = "Rain vs Min Temperature", subtitle = "UK 1853 - 2020",
       x = "Rain Fall C°", y = "Min Temperature C°")
```

##model 3

dependent: sun
Independent: Max Temperature

```{r}
model3 <- lm( tmax ~ sun ,mydata)
test3 <- data.frame(sun = c(7))
predictheat <- predict(model3, test3)
cat("The predicted Sun and max temperature in UK will be", predictheat )
```


```{r}
ggplot(mydata, aes(x = tmax, y = sun))+
  geom_point(aes(color = sun))+
  theme(legend.position = "none")+
  labs(title = "Max Temperature vs Sun", subtitle = "UK 1853 - 2020",
        x = "Max Temperature C°", y = "Sun")
```



##model 4

Discrete 

dependent: air frost
Independent: Month

```{r}
model3 <- lm( month ~ af ,mydata)
test3 <- data.frame(af = c(5))
predictheat <- predict(model3, test3)
cat("The predicted air frost in UK will be", predictheat )
```

af means Days of air frost recorded that month (days)


```{r}
ggplot(mydata, aes(x = month, y = af))+
  geom_point(aes(color = af))+
  theme(legend.position = "none")+
  labs(title = "Month vs  Air Frost", subtitle = "UK 1853 - 2020",
        x = " Month ", y = " Air Frost")
```


##model 5


dependent: Min Temperature
Independent: Max Temperature

```{r}
model3 <- lm( tmax ~ tmin ,mydata)
test3 <- data.frame(tmin = c(4))
predictheat <- predict(model3, test3)
cat("The Min Temp (c) in UK  will be:", predictheat )
```

af means Days of air frost recorded that month (days)


```{r}
ggplot(mydata, aes(x = tmax, y = tmin))+
  geom_point(aes(color = tmin))+
  theme(legend.position = "none")+
  labs(title = "Max Temperature vs  Min Temperature", subtitle = "UK 1853 - 2020",
        x = " Max Temperature ", y = " Min Temperature")
```
